DOpElib - Deal Optimization Environment

### 2012-06-19 Examples/Documentation/introduction.tex
Documentation updated
Updated the manual to include information on the installation on Mac OSX

\texttt{DOpElib} requires a recent \texttt{g++} (at least 4.4.3) due to 
some new \texttt{C++} features implemented in \texttt{C++0x} and \texttt{C++11}.

@@

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE. {\bf FIXME there is something wrong in this file see FIXME 
    comment in the source.}
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\end{itemize}

>>>>

\subsection{g++}
\texttt{DOpElib} requires a recent \texttt{g++} (at least 4.4.3) due to 
some new \texttt{C++} features implemented in \texttt{C++0x} and \texttt{C++11}. 
You can check the version number using the command-line argument \texttt{g++ -v}.

Under Linux-systems this typically means that you have to do nothing if you have a recent 
version number. Otherwise you can either install the required version of g++ using the 
appropriate software installation tool, or you can build the required version from 
source \texttt{gcc.gnu.org}.

Under MAC OSX, you need to install the \texttt{XCode} tools delivered with the operating system 
or availiable for free \texttt{developer.apple.com/xcode}. Unfortunately, the delivered 
version of \texttt{g++} is too old, so you need to install the real thing. To do so, 
download \texttt{MacPorts} from \texttt{macports.org}. Once you have installed MacPorts 
you can use it to install aditional linux software. 
First, update the MacPorts installation \texttt{sudo port selfupdate}
after that you can install a new version of \texttt{g++} using forinstance 
\texttt{sudo port install gcc45} to install version $4.5$ of the compiler.
Afterwards, you need to set the search path appropriate to find the macports version
of \texttt{g++}, to check if this has been done use \texttt{g++ -v}.

@@

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE.
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\end{itemize}
